Ceph Parallel File System Evaluation Report

### 2013-08-29 abstract.tex
minor changes
fix the flow and minor typos

In collaboration with its major developer, Inktank Inc, we evaluated the Ceph
technology for high-performance computing (HPC) environments.  This paper
presents our evaluation methodology, experiments, results and observations from
mostly parallel I/O performance and scalability perspectives.  Our work made
two unique contributions. First, our evaluation is performed under a realistic
setup for a large-scale capability HPC environment like ours using a commercial
high-end storage system.
% (Data Direct Network's SFA10K).
%although typical in large-scale HPC environment, but atypical for average
%commercial off-the-shelf setup.  
Second, our path of investigation, tuning efforts, and findings made direct
contributions to Ceph's development and improved code quality, scalability, and
performance. These changes should also benefit both Ceph and HPC communities at
large. Throughout the evaluation, we observed that Ceph still is an evolving
technology under fast-paced development and showing with great promises.

>>>>

In collaboration with its major developer, Inktank Inc, we evaluated the Ceph
technology for scientific high-performance computing (HPC) environments.  This paper
presents our evaluation methodology, experiments, results and observations from
mostly parallel I/O performance and scalability perspectives.  Our work made
two unique contributions. First, our evaluation is performed under a realistic
setup for a large-scale capability HPC environment like ours using a commercial
high-end storage system.
% (Data Direct Network's SFA10K).
%although typical in large-scale HPC environment, but atypical for average
%commercial off-the-shelf setup.  
Second, our path of investigation, tuning efforts, and findings made direct
contributions to Ceph's development and improved code quality, scalability, and
performance. These changes should also benefit both Ceph and HPC communities at
large. Throughout the evaluation, we observed that Ceph still is an evolving
technology under fast-paced development and showing great promises.

### 2013-08-29 ceph-initial.tex
fix the flow and minor typos

\section{Ceph Evaluation: Initial Results}
\label{sec:ceph-initial}

@@

We observed that using two or more client processes and many concurrent
operations are important when performing these tests.  We tested eight client processes 
with 32 concurrent 4 MB objects in flight each. We created a pool for
each RADOS Bench process to ensure that object reads come from independent pools
(RADOS Bench is not smart enough to ensure that objects are not read by multiple
processes and thus possibly cached).  A sync and flush is performed on every
node before every test to ensure no data or metadata is in cache.  All tests
were run with replication set to one.  The backend file systems were XFS,
BTRFS and EXT4 file systems were not tested at this time.

@@

\subsection{Ceph File System Performance}

@@

  \item The small read (4 KB transfer size) performance is almost an anomaly
  -- we will investigate why it is so low compare to write performance and
  present improved results in Section~\ref{sec:improve-ior}.

@@

@@

The results also show that file creation rate is signficantly lower than
directory creation rate. We stipulated two contributing factors: one is the file
creation is associated with 1 MB data write and followed by a fsync operation,
which is a rather heavy weight operation compare to directory creation. Another
factor is that we obtained above results while both RADOS and file
system-level performance are not tuned for optimal, yet.

>>>>

\section{Ceph Evaluation: Initial Results and Tunings}
\label{sec:ceph-initial}

@@

\subsubsection{Disable TCP autotuning}

\begin{figure}[htb]
\centering
%\includegraphics[width=3.5in]{rados-after-ddn-tcptune}
\includegraphics[width=3.5in]{autotune-enabled}
\caption{Evaluating RADOS bench \textbf{with} TCP auto tuning, 4 servers, 4
clients, 4 MB I/O}
\label{fig:rados-tcp-autotune}
\end{figure}

During our early tests, a trend that previously had been seen became more
apparent.  During reads, there were periods of high performance followed by
periods of low performance or outright stalls that could last for up to 20
seconds at a time.  RADOS bench recorded poor read performance across
different backend file systems, as shown in
Figure~\ref{fig:rados-tcp-autotune}.

After running diagnostics, we observed that outstanding operations on the
clients were not being shown as outstanding on the OSDs.  This appeared to be
very similar to a problem Jim Schutt at Sandia National labs encountered with
TCP autotuning in the Linux
kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}
TCP auto tuning enables TCP window scaling by default and automatically adjusts
the TCP receive window for each connection based on link conditions such as
bandwidth delay product. We have observed this improving the performance
significantly on Ceph read operations. As shown in
Figure~\ref{fig:rados-tcp-autotune-disabled}.

Luckily, the fix was fairly straight forward by issuing the following command
on all nodes:

\begin{Verbatim}[fontsize=\small]
 echo 0 | sudo tee 
   /proc/sys/net/ipv4/tcp_moderate_rcvbuf
\end{Verbatim}

Recent versions of Ceph work around this issue by manually controlling the TCP
buffer size.

\begin{figure}[htb]
\centering
%\includegraphics[width=3.5in]{rados-after-ddn-tcptune}
\includegraphics[width=3.5in]{autotune-disabled}
\caption{Evaluating RADOS bench with TCP auto tuning \textbf{disabled},  4 servers, 4
clients, 4 MB I/O}
\label{fig:rados-tcp-autotune-disabled}
\end{figure}

We also observed that using two or more client processes and many concurrent
operations are important when performing these tests.  We tested eight client
processes with 32 concurrent 4 MB objects in flight each. We created a pool
for each RADOS Bench process to ensure that object reads come from independent
pools (RADOS Bench is not smart enough to ensure that objects are not read by
multiple processes and thus possibly cached).  A sync and flush is performed
on every node before every test to ensure no data or metadata is in cache.
All tests were run with replication set to one.

@@

\subsection{Ceph File System Performance}
\label{sec:ior-initial}

@@

  \item The small read (4 KB transfer size) performance is almost an anomaly

@@

The bottom line is, though we have obtained decent performance number at RADOS
level, but it did not translate into file system-level performance. We will
investigate why it is so low compare to write performance and present improved
results in Section~\ref{sec:ceph-tuning}.

@@

The results also show that file creation rate is significantly lower than
directory creation rate. We stipulated two contributing factors: one is the file
creation is associated with 1 MB data write and followed by a fsync operation,
which is a rather heavy weight operation compare to directory creation. Another
factor is that we obtained above results while both RADOS and file
system-level performance are not tuned for optimal, yet.

### 2013-08-29 ceph-tuning.tex
update bar drawing to be the same style
fix the flow and minor typos

\section{Tuning, Optimization and Improvements}
\label{sec:ceph-tuning}

@@

\subsubsection{Disable TCP autotuning}

During these tests, a trend that previously had been seen became more apparent.
During reads, there were periods of high performance followed by periods of low
performance or outright stalls that could last for up to 20 seconds at a time.
After running diagnostics, we observed that outstanding operations on the
clients were not being shown as outstanding on the OSDs.  This appeared to be
very similar to a problem Jim Schutt at Sandia National labs encountered with
TCP autotuning in the Linux
kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}
TCP auto tuning enables TCP window scaling by default and automatically adjusts
the TCP receive window for each connection based on link conditions such as
bandwidth delay product. We have observed this improving the performance
significantly on Ceph read operations, as the results shown in
Figure~\ref{fig:rados-tcp-auto-disabled}.

Luckily, the fix was fairly straight forward by issuing the following command
on all nodes:

\begin{Verbatim}[fontsize=\small]
 echo 0 | sudo tee 
   /proc/sys/net/ipv4/tcp_moderate_rcvbuf
\end{Verbatim}

Recent versions of Ceph work around this issue by manually controlling the TCP
buffer size.

\begin{figure}[htb]
\centering
\includegraphics[width=3.5in]{rados-after-ddn-tcptune}
\caption{Evaluating RADOS bench after TCP auto tuning disabled}
\label{fig:rados-tcp-auto-disabled}
\end{figure}

%\begin{figure}[htb]
%\includegraphics[width=5in]{rados-064-oss}
%\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=3.5in]{ior-client-no-crc32}
\caption{IOR test with disabling client-side CRC32}
\label{fig:ior-no-client-crc32}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=3.5in]{rados-kernel-35vs39}
\caption{RADOS bench: Linux kernel version 3.5 vs. 3.9}
\label{fig:rados-kernel}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=3.5in]{ior-kernel-39}
\caption{CephFS performance with kernel changes to 3.9, IOR with 4 MB transfer
size}
\label{fig:ior-kernel-39}
\end{figure}

>>>>

\section{Further Optimization and Improvements}
\label{sec:ceph-tuning}

@@

@@

\begin{figure}[htb]
\centering
%\includegraphics[width=3.5in]{ior-client-no-crc32}
\includegraphics[width=3.5in]{ior_no_crc}
\caption{IOR test with disabling client-side CRC32}
\label{fig:ior-no-client-crc32}
\end{figure}

@@

\begin{figure}[htb]
\centering
%\includegraphics[width=3.5in]{rados-kernel-35vs39}
\includegraphics[width=3.5in]{rados_kernel}
\caption{RADOS bench: Linux kernel version 3.5 vs. 3.9}
\label{fig:rados-kernel}
\end{figure}

@@

\begin{figure}[htb]
\centering
%\includegraphics[width=3.5in]{ior-kernel-39}
\includegraphics[width=3.5in]{ior_kernel_change}
\caption{CephFS performance with kernel changes to 3.9, IOR with 4 MB transfer
size}
\label{fig:ior-kernel-39}
\end{figure}
